Forecasting US Presidential Election Results Using Bayesian Prediction

### 2024-11-04 paper/paper.qmd
Update and rename paper_FV1.qmd to paper.qmd

The paper is structured as follows: @sec-data introduces data preparation and variable description, using data from FiveThirtyEight’s U.S [@FiveThirtyEight_Polls]. Presidential election polls were collected from pollsters with a focus on the percentage of support rates and indicators of opinion poll agencies. Then, @sec-Model defined and fitted a Bayesian model to estimate the candidate's support rate, which can reduce the uncertainty of quantitative parameters through posterior distribution, enhance the credibility of analysis results, and allow the introduction of prior information to improve accuracy. @sec-Results presents the results, highlighting trends in polling, and @sec-Discussion considers the implications of these results for future research on polling and the weakness of the research.
```{r, quiet=TRUE}
#| warning: false
#| message: false
#| echo:    false
poll_of_polls <- read.csv("analysis_data.csv")
```
# Data {#sec-data}

This project is motivated and guided by Rohan Alexander and his book [@tellingstories]. All the data used in this paper is derived from FiveThirtyEight’s U.S. [@FiveThirtyEight_Polls], and all the data analysis was done through the programming language **R** [@citeR]. Also with the support of additional packages in R: `ggplot2` [@citeGgplot2], `rstan`  [@citeRstan], `dplyr` [@citeDplyr], `here` [@citeHere], `knitr` [@citeKnitr].

## Source

The dataset analyzed in this paper is to study poll of poll data to obtain more information about presidential elections [@FiveThirtyEight_Polls]. The Poll of Polls is a comprehensive dataset that combines public surveys from multiple pollsters, including key data such as methodology, states, and answers used by each pollster that was collected on October 20, 2024. We did not do tail reduction, deletion, or other processing on the raw data to ensure data integrity. The dataset is a compilation of public opinion poll results from various institutes. It covers terms like pollster, state, pollster rating, and response. We utilized some parts of the data in this study.

>>>>

The paper is structured as follows: @sec-data introduces data preparation and variable description, using data from FiveThirtyEight’s U.S [@FiveThirtyEight_Polls]. Presidential election polls were collected from pollsters with a focus on the percentage of support rates and indicators of opinion poll agencies. Then, @sec-Model defined and fitted a Bayesian model to estimate the candidate's support rate, which can reduce the uncertainty of quantitative parameters through posterior distribution, enhance the credibility of analysis results, and allow the introduction of prior information to improve accuracy. @sec-Results presents the results, highlighting trends in polling, and @sec-Discussion considers the implications of these results for future research on polling and the weakness of the research.

This project is motivated and guided by Rohan Alexander and his book [@tellingstories]. All the data used in this paper is derived from FiveThirtyEight’s U.S. [@FiveThirtyEight_Polls], and all programming for this paper was done through the programming language **R** [@citeR]. Also with the support of additional packages in R: `ggplot2` [@citeGgplot2], `rstan`  [@citeRstan], `dplyr` [@citeDplyr], `here` [@citeHere], `knitr` [@citeKnitr].
```{r, quiet=TRUE}
#| warning: false
#| message: false
#| echo:    false
poll_of_polls <- read.csv("analysis_data.csv")
```
# Data {#sec-data}

## Overview

The data analyzed in this paper is to study poll of poll data to obtain more information about presidential elections [@FiveThirtyEight_Polls]. The Poll of Polls is a comprehensive data that combines public surveys from multiple pollsters, including key data such as methodology, states, and answers used by each pollster that was collected on October 20, 2024. The data is a compilation of public opinion poll results from various institutes. It covers terms like pollster, state, pollster rating, and response. We utilized some parts of the data in this study.

## Measurement

The data reflects the views of the American public on the 2024 U.S. Presidential election, collected through opinion polls conducted by various organizations. These polls ask people which candidate they plan to support, as well as some other personal information, using methods such as online surveys or phone interviews, and accurately record the information.

Once this data is collected, it’s cleaned to ensure accuracy, removing any entries with missing values. This makes our dataset efficient and reliable.
